---
title: "Caliban Tutorial"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is Caliban?

### Caliban is

    - a tool to launch and track numerical experiments in a computing environment

    - go from a prototype to thousands of experimental jobs running on the Cloud

    - developed by machine learning researchers and engineers


### Train a neural network on the local machine

  - train an image classification network (implemented in TensorFlow)

  - increase model's accuracy by changing the learning rate

  - sweep across a range of learning rates

  - train the model in the cloud on Google's AI Platform

  - develop code using caliban shell


## Installation

### 1. In terminal:

```{r example1, eval=FALSE}
pip install caliban
```

### 2. Get docker:

  <https://hub.docker.com/editions/community/docker-ce-desktop-mac>


### 3. Set up google cloud account:

  <https://caliban.readthedocs.io/en/latest/getting_started/cloud.html>


### 4. Install google cloud SDK in terminal:

```{r example4, eval=FALSE}
./google-cloud-sdk/install.sh

gcloud init
```

### 5. Create Enviroment Variables:

  a. set up **.zshrc** (or .bash_profile)
  
```{r example5, eval=FALSE}
nano.zshrc
```

  b. add following variables:

```{r example6, eval=FALSE}
./google-cloud-sdk/install.sh

export PROJECT_ID=<your-project-id>

export GOOGLE_APPLICATION_CREDENTIALS=$HOME/.config/service_key.json

```


## Training Neural Networks

### 1. Setup:

```{r example7, eval=FALSE}
mkdir demo && cd demo

curl --output mnist.py https://raw.githubusercontent.com/google/caliban
    master/tutorials/basic/mnist.py

echo "tensorflow-cpu" > requirements.txt
```


### 2. Train a basic neural network

```{r example8, eval=FALSE}
caliban run --nogpu mnist.py
```

*Training model with learning rate=0.1 for 3 epochs*
*accuracy: 0.2328*


### 3. Improve Model:

```{r example9, eval=FALSE}

caliban run --nogpu mnist.py -- --learning_rate 0.01
```
*accuracy: 0.9549!!!*

### 4. Experiment Brodcasting: 

  a. create a .json file in terminal

```{r example10, eval=FALSE}
echo '{"learning_rate": [0.01, 0.001, 0.0001]}' > experiment.json`
```

  b. run following command with configuration in **terminal**

```{r example10a, eval=FALSE}
caliban run --experiment_config experiment.json --nogpu mnist.py
```


### 5. Submitting to Cloud AI Platform:

```{r example11, eval=FALSE}
gcloud config set project prickly-cactus

caliban cloud --nogpu mnist.py -- --learning_rate 0.01
```

    what caliban is doing:

    - building a Docker container with all of your code

    - moving that container to google cloud's container registry
  
    - submitting the job to AI Platform


6. Caliban Shell:
